\Title

### 2021-08-24 manuscript/content.tex
Shrink figure on preprint due to onecolumn
Some tweaks to the preprint styling (#167)
* Some tweaks to the preprint styling

Decreased margins (to save space), increase column separation (better
readability), tweak figure placement, and remove the footer (the header
has the citation info, which is what's important).

* Increase margins to 1.5cm

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>
Use the mGal variable in manuscript

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosted equivalent source algorithm.
        Data points are represented by blue upwards-facing triangles,
        equivalent sources by orange dots, data residuals by red downwards-facing
        triangles, and the current window by black dashed lines.
        The algorithm starts by selecting the data and sources
        inside the first window and estimating the source coefficients
        using the selected data points.
        Then, the effect of the estimated sources is predicted on all data
        points and used to calculate the residuals.
        Another window is used to select residuals and sources and
        estimate the coefficients using the selected residuals instead of the
        original data.
        Again, the effect of the estimated sources is predicted on all data points
        and the residuals are updated.
        These steps are repeated for every window in a randomized order.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Sketch of different horizontal layouts for equivalent source models.
        Blue points represent the locations of observations and orange points
        represent the locations of equivalent sources according to different
        layout strategies.
        (a)~Set of \SourceLayoutsSchematicsObservations{} observation points
        that simulate a ground survey.
        (b)~Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
        obtained through the \emph{sources below data} layout.
        (c)~Location of the \SourceLayoutsSchematicsGridSources{} sources
        obtained through the \emph{regular grid} layout.
        (d)~Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
        sources obtained through the \emph{block-averaged sources} layout.
        Grey dashed lines represent the spatial blocks within which the median
        observation location is calculated.
    }
    \label{fig:source_layouts}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Examples of different strategies for assigning depths to equivalent
        sources.
        Here we assign one source for each
        observation point, located at the same horizontal coordinates as the
        data points.
        Source depths are
        (a)~a \emph{constant depth} at a chosen vertical coordinate,
        (b)~a \emph{relative depth} determined by uniformly shifting downward
        the vertical coordinate of data points,
        and
        (c)~a \emph{variable depth} determined by shifting the vertical
        coordinates of the observation points by an amount proportional to the
        average distance to neighbouring sources.
        The distance between data points and their respective sources (a)
        depends on observation height, (b) is constant, and (c) is proportional
        to the horizontal distribution of sources.
        Notice how the closely spaced sources in the middle of the profile (c)
        are shallower than their counterparts in (b).
    }
    \label{fig:depth_types}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Observation heights and gravity values for the synthetic ground (a-b)
        and airborne (c-d) surveys.
        Heights are given in meters above the zero height plane.
        The synthetic gravity data are contaminated with pseudo-random Gaussian
        noise with zero mean and \SurveyNoise{} standard deviation.
    }
    \label{fig:synthetic-layouts}
\end{figure*}

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Pseudo-color map of the target grid of synthetic gravity data. The grid
        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
        above the zero height plane.
    }
    \label{fig:synthetic-target}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic ground survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic airborne survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Interpolation RMS error (a-b) and relative computation time (c-d) for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Window overlap is given as a percentage of the window size (an overlap
        of 50\% means that two adjacent windows share an area half of the size
        of the entire window).
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars are 1 standard deviation) of results using different
        seeds for the pseudo-random number generator.
        Computation time is the ratio between the time required to estimate the
        source coefficients for the gradient-boosted and the regular equivalent
        sources.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

@@

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Interpolation error for gradient-boosted equivalent sources using
        randomized (a) and sequential (b) window order.
        (a and b)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data.
        The color scale has been cropped to the same range as
        Fig.~\ref{fig:airborne-survey-differences}.
        (c)~Root-mean squared error after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/australia.png}
    \caption{
      Pseudo-color maps of observed (a and c) and
      interpolated (b and d) gravity disturbance of Australia.
      The observed values in a and c are plotted as colored circles.
      The red rectangle marks the boundaries of the highlight maps in c
      and d.
      Observations are part of a compilation by \citet{wynne2018} of
      over 1.7 million ground gravity measurements.
      Interpolated values were obtained through gradient-boosted equivalent
      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
      over the WGS84 ellipsoid.
    }
    \label{fig:australia}
\end{figure*}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix for different window sizes. Our implementation uses double
        precision floating point numbers (64 bits) for the Jacobian.
        (b) Root-mean square error against the observed data after each
        iteration of the gradient-boosting algorithm.
        (c) K-Fold cross-validation root-mean square errors obtained for each
        pair of damping and depth parameters. The orange star highlights the
        minimum.
    }
    \label{fig:australia-memory-cv-error}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/australia-residuals.png}
    \caption{
        Residuals. Differences between the gravity disturbance data from
        Australia and the predicted values by the estimated equivalent sources
        on the same observation points. The color map has been truncated to
        improve the visualization around the largest portion of residual
        values. The inset plot shows a histogram of the residuals.
    }
    \label{fig:australia-residuals}
\end{figure}

@@

The largest residuals in Fig.~\ref{fig:australia-residuals} are located in
regions with high-amplitude short-wavelength features in the observed data.
This is expected since the method involves some degree of smoothing because of
the use of damping and the source depths.
There are also low-amplitude long-wavelength residual signals that seem to
coincide with some of the windows of the gradient-boosting method.
A possible cause of these features is inability of the equivalent-sources
within a window to adequately fit the long-wavelength components of the data.
We note, however, that all of these long-wavelength residuals are smaller than
1 mGal in amplitude and do not represent a significant source of errors.

>>>>

\begin{figure*}[tb]
    \centering
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosted equivalent source algorithm.
        Data points are represented by blue upwards-facing triangles,
        equivalent sources by orange dots, data residuals by red downwards-facing
        triangles, and the current window by black dashed lines.
        The algorithm starts by selecting the data and sources
        inside the first window and estimating the source coefficients
        using the selected data points.
        Then, the effect of the estimated sources is predicted on all data
        points and used to calculate the residuals.
        Another window is used to select residuals and sources and
        estimate the coefficients using the selected residuals instead of the
        original data.
        Again, the effect of the estimated sources is predicted on all data points
        and the residuals are updated.
        These steps are repeated for every window in a randomized order.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}

@@

\begin{figure*}[tb]
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Sketch of different horizontal layouts for equivalent source models.
        Blue points represent the locations of observations and orange points
        represent the locations of equivalent sources according to different
        layout strategies.
        (a)~Set of \SourceLayoutsSchematicsObservations{} observation points
        that simulate a ground survey.
        (b)~Location of the \SourceLayoutsSchematicsSourceBelowData{} sources
        obtained through the \emph{sources below data} layout.
        (c)~Location of the \SourceLayoutsSchematicsGridSources{} sources
        obtained through the \emph{regular grid} layout.
        (d)~Location of the \SourceLayoutsSchematicsBlockAveragedSources{}
        sources obtained through the \emph{block-averaged sources} layout.
        Grey dashed lines represent the spatial blocks within which the median
        observation location is calculated.
    }
    \label{fig:source_layouts}
\end{figure*}

@@

\begin{figure*}[tb]
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Examples of different strategies for assigning depths to equivalent
        sources.
        Here we assign one source for each
        observation point, located at the same horizontal coordinates as the
        data points.
        Source depths are
        (a)~a \emph{constant depth} at a chosen vertical coordinate,
        (b)~a \emph{relative depth} determined by uniformly shifting downward
        the vertical coordinate of data points,
        and
        (c)~a \emph{variable depth} determined by shifting the vertical
        coordinates of the observation points by an amount proportional to the
        average distance to neighbouring sources.
        The distance between data points and their respective sources (a)
        depends on observation height, (b) is constant, and (c) is proportional
        to the horizontal distribution of sources.
        Notice how the closely spaced sources in the middle of the profile (c)
        are shallower than their counterparts in (b).
    }
    \label{fig:depth_types}
\end{figure*}

@@

\begin{figure*}[tb]
    \includegraphics[width=\linewidth]{figs/synthetic-survey-layouts.pdf}
    \caption{
        Observation heights and gravity values for the synthetic ground (a-b)
        and airborne (c-d) surveys.
        Heights are given in meters above the zero height plane.
        The synthetic gravity data are contaminated with pseudo-random Gaussian
        noise with zero mean and \SurveyNoise{} standard deviation.
    }
    \label{fig:synthetic-layouts}
\end{figure*}

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Pseudo-color map of the target grid of synthetic gravity data. The grid
        is composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{}. The grid height is \TargetHeight{}
        above the zero height plane.
    }
    \label{fig:synthetic-target}
\end{figure}

@@

\begin{figure*}[p]
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic ground survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}[p]
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Pseudo-color maps of the differences between the target grid and the
        interpolated synthetic airborne survey data produced by each source
        distribution strategy.
        The black dots represent the horizontal location of the synthetic data
        points. The RMS error and total number of equivalent sources is
        reported for each strategy at the top of the respective maps.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

@@

\begin{figure*}[tb]
    \includegraphics[width=\linewidth]{figs/gradient-boosted-comparisons.pdf}
    \caption{
        Interpolation RMS error (a-b) and relative computation time (c-d) for
        regular least-squares equivalent sources (orange dashed lines) and
        gradient-boosted equivalent sources (blue dots and error bars).
        Window overlap is given as a percentage of the window size (an overlap
        of 50\% means that two adjacent windows share an area half of the size
        of the entire window).
        For gradient-boosting, the RMS errors and computation times are the
        means (error bars are 1 standard deviation) of results using different
        seeds for the pseudo-random number generator.
        Computation time is the ratio between the time required to estimate the
        source coefficients for the gradient-boosted and the regular equivalent
        sources.
}
    \label{fig:gradient-boosted-comparison}
\end{figure*}

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Interpolation error for gradient-boosted equivalent sources using
        randomized (a) and sequential (b) window order.
        (a and b)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data.
        The color scale has been cropped to the same range as
        Fig.~\ref{fig:airborne-survey-differences}.
        (c)~Root-mean squared error after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}

@@

@@

\begin{figure*}[p]
    \includegraphics[width=\linewidth]{figs/australia.png}
    \caption{
      Pseudo-color maps of observed (a and c) and
      interpolated (b and d) gravity disturbance of Australia.
      The observed values in a and c are plotted as colored circles.
      The red rectangle marks the boundaries of the highlight maps in c
      and d.
      Observations are part of a compilation by \citet{wynne2018} of
      over 1.7 million ground gravity measurements.
      Interpolated values were obtained through gradient-boosted equivalent
      sources and calculated on a regular grid at \AustraliaEqlGridHeight{}
      over the WGS84 ellipsoid.
    }
    \label{fig:australia}
\end{figure*}

@@

\begin{figure}[tbh!]
    \makeatletter%
    \if@twocolumn%
        \includegraphics[width=\linewidth]{figs/australia-memory-cv-error.pdf}
    \else% \@twocolumnfalse
        \centering
        \includegraphics[width=0.6\linewidth]{figs/australia-memory-cv-error.pdf}
    \fi
    \makeatother
    \caption{
        (a) Amount of computer memory needed to store the largest Jacobian
        matrix for different window sizes. Our implementation uses double
        precision floating point numbers (64 bits) for the Jacobian.
        (b) Root-mean square error against the observed data after each
        iteration of the gradient-boosting algorithm.
        (c) K-Fold cross-validation root-mean square errors obtained for each
        pair of damping and depth parameters. The orange star highlights the
        minimum.
    }
    \label{fig:australia-memory-cv-error}
\end{figure}

@@

\begin{figure}[tb]
    \includegraphics[width=\linewidth]{figs/australia-residuals.png}
    \caption{
        Residuals. Differences between the gravity disturbance data from
        Australia and the predicted values by the estimated equivalent sources
        on the same observation points. The color map has been truncated to
        improve the visualization around the largest portion of residual
        values. The inset plot shows a histogram of the residuals.
    }
    \label{fig:australia-residuals}
\end{figure}

@@

The largest residuals in Fig.~\ref{fig:australia-residuals} are located in
regions with high-amplitude short-wavelength features in the observed data.
This is expected since the method involves some degree of smoothing because of
the use of damping and the source depths.
There are also low-amplitude long-wavelength residual signals that seem to
coincide with some of the windows of the gradient-boosting method.
A possible cause of these features is inability of the equivalent-sources
within a window to adequately fit the long-wavelength components of the data.
We note, however, that all of these long-wavelength residuals are smaller than
1\mGal{} in amplitude and do not represent a significant source of errors.
